Analysis Report

### 2019-10-28 analysis/analysis_report.rmd
revised submission

@@

source(here::here("R", "dz_calculator.r"))
source(here::here("R", "vmac_pal.R"))
source(here::here("R", "summarySEwithin2.r"))

@@

@@

@@

save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

@@

feature_physicalsalience_omissions.ttest <- t.test(feature_absent_omissions, feature_low_omissions, paired = T) # reverse the order here so can get positive t value
feature_physicalsalience_omissions.ttest
feature_physicalsalience_omissions.es <- dz_calculator(feature_low_omissions, feature_absent_omissions)
feature_physicalsalience_omissions.es
```

@@

saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1))

@@

save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)

@@

@@

save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

@@

save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

@@

>>>>

afex_options(emmeans_model = "multivariate")

@@

source(here::here("R", "dz_calculator.r"))
source(here::here("R", "ds_calculator.r"))
source(here::here("R", "vmac_pal.R"))
source(here::here("R", "summarySEwithin2.r"))
source(here::here("R", "remove_lz.R"))

@@

awaredata <- filedata %>%
  map(27)  %>% 
  modify(as.data.frame)

index_removed_awaredata <- which(sapply(awaredata, nrow) < 4)

awaredata <- awaredata[-index_removed_awaredata]

awaredata <- Map(cbind, awaredata, sub = subNums[-index_removed_awaredata]) %>% 
  bind_rows()

colnames(awaredata)[1:5] <- c("question_type", "trial_counter", "colour", "clicked_button", "confidence_rating")

awaredata$question_type <- factor(awaredata$question_type, labels = c("to_target", "to_distractor"))
awaredata$colour <- factor(awaredata$colour, labels = c("high", "low"))

@@

```{r Prepare data for repetition priming analysis}
exptdata <- exptdata %>%
  mutate(singleton_present = case_when(distractType == 1 | distractType == 2 ~ 1,
                                       TRUE ~ 0)) %>% 
  mutate(singleton_repetition = case_when(singleton_present == lag(singleton_present) & distractType != 3 ~ 1,
                                          TRUE ~ 0))

@@

# save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

@@

feature_physicalsalience_omissions.ttest <- t.test(feature_absent_omissions, feature_low_omissions, paired = T) # reverse the order here so can get positive t value
feature_physicalsalience_omissions.ttest
feature_physicalsalience_omissions.es <- dz_calculator(feature_low_omissions, feature_absent_omissions)
feature_physicalsalience_omissions.es

Exploratory analyses following reviews:
```{r}
absent_singleton_vs_feature.ttest <- t.test(feature_absent_omissions, singleton_absent_omissions, var.equal = T)
absent_singleton_vs_feature.ttest
absent_singleton_vs_feature.es <- ds_calculator(feature_absent_omissions, singleton_absent_omissions)
absent_singleton_vs_feature.es

low_singleton_vs_feature.ttest <- t.test(singleton_low_omissions,feature_low_omissions, var.equal = T)
low_singleton_vs_feature.ttest
low_singleton_vs_feature.es <- ds_calculator(singleton_low_omissions, feature_low_omissions)
```

@@

saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2.2,1,.1))

@@

 # save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2.2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)

@@

Singleton_low.ttestBF_onesided <- captureData_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Singleton Search") %>%
  filter(dType == "Low") %>%
  select(Capture) %>%
  pull() %>%
  ttestBF(nullInterval = c(0,Inf))

Singleton_low.ttestBF_directional <- Singleton_low.ttestBF_onesided[1]/Singleton_low.ttestBF_onesided[2]

Singleton_low.ttestBF_onesided_2 <- captureData_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Singleton Search") %>%
  filter(dType == "Low") %>%
  select(Capture) %>%
  pull() %>%
  ttestBF(nullInterval = c(0,-Inf))

1/Singleton_low.ttestBF_onesided_2

@@

# save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

@@

# save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1.2, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)

@@

## Repetition priming effects

```{r Repetition Priming Plots}

saccadeData_means_bysingletonrepetition <- 
  saccadedata %>%
  mutate(sub = as.factor(sub)) %>%
  filter(dType != "Absent") %>% 
  group_by(sub, condition, singleton_repetition, dType) %>%
  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
            capture = saccade_to_singleton - saccade_to_nonsingleton,
            n = n())

# capture_singleton_repetition.ANOVA <- aov_car(capture ~ singleton_repetition*condition*dType + Error(sub/singleton_repetition*dType), data = saccadeData_means_bysingletonrepetition, anova_table = list(es="pes"))

#knitr::kable(nice(capture_singleton_repetition.ANOVA))

capturemeans_bysingletonrepetition <- summarySEwithin2(data = saccadeData_means_bysingletonrepetition, measurevar = "capture", betweenvars = "condition", withinvars = c("singleton_repetition"), idvar = "sub", na.rm = T) %>%
  select(-ends_with("Normed"))

capturemeans_bysingletonrepetition_individual <- saccadeData_means_bysingletonrepetition %>% 
  ungroup() %>% 
  group_by(sub, condition, singleton_repetition) %>% 
  select(capture) %>% 
  summarize(m_capture = mean(capture))

capturemeans_bysingletonrepetition_individual$singleton_repetition <- factor(capturemeans_bysingletonrepetition_individual$singleton_repetition)

average_singleton_repetition <- saccadeData_means_bysingletonrepetition %>% 
  ungroup() %>% 
  group_by(singleton_repetition) %>% 
  summarise(mean_n = mean(n))

singleton_repetition_singleton_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Singleton Search"), aes(x = singleton_repetition, y = capture, group = 1)) +
  geom_path() +
  geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Singleton Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) + 
  geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) +
  geom_point(size = 3) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) +
  labs(y = "Capture Score", x= "", tag = "A", title = "Singleton Search") +
  #lims(y = c(-.2, .3)) +
  scale_color_manual(values = vmacCols) +
  scale_x_discrete(labels = c("No-repeat", "Repeat")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) +
  my_theme +
  theme(strip.text = element_text(face = "bold"))

singleton_repetition_feature_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Feature Search"), aes(x = singleton_repetition, y = capture, group = 1)) +
  geom_path() +
  geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Feature Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) + 
  geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) +
  geom_point(size = 3) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) +
  labs(y = "Capture Score", x= "", tag = "B", title = "Feature Search") +
  #lims(y = c(-.2, .3)) +
  scale_color_manual(values = vmacCols) +
  scale_x_discrete(labels = c("No-repeat", "Repeat")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) +
  my_theme +
  theme(strip.text = element_text(face = "bold"))

singleton_repetition_plot_horz <- plot_grid(singleton_repetition_singleton_search_plot, singleton_repetition_feature_search_plot, align = 'vh')
# singleton_repetition_plot_horz <- ggdraw(add_sub(singleton_repetition_plot_horz, "Singleton Repetition", fontfamily = font_rc, vpadding=grid::unit(0,"lines"), y = 6, x = 0.55, vjust = 4.5))

# plot_grid(singleton_repetition_plot_horz, title, ncol = 1, rel_heights = c(1,.1))

# save_plot(here::here("analysis", "figures", "singleton_repetition_priming.png"), singleton_repetition_plot_horz, type = "cairo", ncol = 1.3, nrow = 1)

```{r Repetition Priming Statistics} 
capture_singleton_repetition.ANOVA <- aov_car(capture ~ singleton_repetition*condition*dType + Error(sub/singleton_repetition*dType), data = saccadeData_means_bysingletonrepetition, anova_table = list(es="pes"))

knitr::kable(nice(capture_singleton_repetition.ANOVA))

saccadeData_means_bysingletonrepetition_no_dtype <- 
  saccadedata %>%
  mutate(sub = as.factor(sub)) %>%
  filter(dType != "Absent") %>% 
  group_by(sub, condition, singleton_repetition) %>%
  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
            capture = saccade_to_singleton - saccade_to_nonsingleton,
            n = n())

capture_singleton_repetition_no_dtype.ANOVA <- aov_car(capture ~ singleton_repetition*condition + Error(sub/singleton_repetition), data = saccadeData_means_bysingletonrepetition_no_dtype, anova_table = list(es="pes"))

singleton_search_no_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
  filter(condition == "Singleton Search", singleton_repetition == 0) %>% 
  pull(capture)

singleton_search_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
  filter(condition == "Singleton Search", singleton_repetition == 1) %>% 
  pull(capture)

singleton_search_singleton_repetition.ttest <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
  filter(condition == "Singleton Search") %>% 
  t.test(formula = capture ~ singleton_repetition, data = ., paired = T)

singleton_search_singleton_repetition.es <- dz_calculator(singleton_search_repeat, singleton_search_no_repeat)

feature_search_no_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
  filter(condition == "Feature Search", singleton_repetition == 0) %>% 
  pull(capture)

feature_search_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
  filter(condition == "Feature Search", singleton_repetition == 1) %>% 
  pull(capture)

feature_search_singleton_repetition.ttest <- t.test(x = feature_search_repeat, y = feature_search_no_repeat, paired = T)

feature_search_singleton_repetition.es <- dz_calculator(feature_search_repeat, feature_search_no_repeat)

feature_search_singleton_repetition.BF <- ttestBF(x = feature_search_repeat, y = feature_search_no_repeat, paired = T)

Summarising these findings: there is an effect of singleton repetition (where capture is reduced following a trial in which a singleton of any identity was presented) for singleton-search mode, but not feature search mode.

```{r Contingency belief score data prep}
awaredata <- awaredata %>%
  mutate(accuracy = case_when(colour == "high" & clicked_button == 3 & question_type == "to_target" ~ 1,
                              colour == "low" & clicked_button == 2 & question_type == "to_target" ~ 1,
                              question_type == "to_distractor" & clicked_button == 1 ~ 1,
                              TRUE ~ 0)) %>%
  mutate(belief_score = case_when(accuracy == 1 ~ confidence_rating,
                                  TRUE ~ -confidence_rating))

captureData_means_byparticipant$sub_num <- as.numeric(as.character(captureData_means_byparticipant$sub))

awareness_scores <- right_join(awaredata, captureData_means_byparticipant, by = c("sub" = "sub_num")) %>%
  filter(question_type == "to_distractor")

awareness_scores_totarget <- right_join(awaredata, captureData_means_byparticipant, by = c("sub" = "sub_num")) %>%
  filter(question_type == "to_target")

```{r Reward contingency belief data}
high_reward_awareness.cor <- awareness_scores_totarget %>% 
  filter(dType == "High", colour == "high") %>% 
  cor.test(~ Capture + belief_score, data = .)

high_reward_contingency_plot <- awareness_scores_totarget %>%
  filter(dType == "High", colour == "high") %>%
  ggplot(aes(x = belief_score, y = Capture)) +
         geom_point(aes(shape = condition), alpha = .5, size = 3) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
  scale_shape_manual(values = c(20,4))+
  labs(x = "Reward contingency belief score", subtitle = "High reward") +
  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
  my_theme +
  guides(shape = guide_legend(title = "Condition", override.aes = list(alpha = 1))) +
  theme(axis.ticks.x = element_line(),
        legend.position = "bottom")

contingency_legend <- get_legend(high_reward_contingency_plot)

high_reward_contingency_plot <- high_reward_contingency_plot +
  theme(legend.position = "none")

low_reward_awareness.cor <- awareness_scores_totarget %>% 
  filter(dType == "Low", colour == "low") %>% 
  cor.test(~ Capture + belief_score, data = .)

low_reward_contingency_plot <- awareness_scores_totarget %>%
  filter(dType == "Low", colour == "low") %>%
  ggplot(aes(x = belief_score, y = Capture)) +
         geom_point(aes(shape = condition), alpha = .5, size = 3) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
  scale_shape_manual(values = c(20,4))+
  labs(x = "Reward contingency belief score", subtitle = "Low reward") +
  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
  my_theme +
  theme(axis.ticks.x = element_line())

reward_contingency_plots <- plot_grid(high_reward_contingency_plot, low_reward_contingency_plot)

reward_contingency_plots_legend <- plot_grid(reward_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)

# save_plot(here::here("analysis", "figures", "reward_contingency_plot.png"), reward_contingency_plots_legend, ncol = 1.4, nrow = 1.1, type = "cairo")

# Count people who reported correct colour--reward relationships for each distractor type:
reward_awareness <- awareness_scores_totarget %>%
    group_by(dType,colour) %>%
    count(accuracy) %>%
  mutate(accuracy = case_when(accuracy == 0 ~ "correct",
                              TRUE ~ "incorrect")) %>% 
    pivot_wider(names_from = accuracy, values_from = n) %>% 
  mutate(total = correct + incorrect) %>% 
  filter(dType == "High") %>% 
  ungroup() %>% 
  select(-dType)

```{r Omission contingency belief data}

# Test for significant correlation b/w awareness test for omission contingency with high-val colour and capture by high-val colour

high_omission_awareness.cor <- awareness_scores %>%
  filter(question_type == "to_distractor", dType == "High", colour == "high") %>%
  cor.test(~ Capture + belief_score, data = .)

high_omission_contingency_plot <- awareness_scores %>%
  filter(dType == "High", colour == "high") %>%
  ggplot(aes(x = belief_score, y = Capture)) +
         geom_point(aes(shape = condition), alpha = .5, size = 3) +
  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
  scale_shape_manual(values = c(20,4))+
  labs(x = "Omission contingency belief score", subtitle = "High reward") +
  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_omission_awareness.cor$estimate, 3), "***"), geom = "text", size = 5, family = font_rc, hjust = 0) +
  my_theme +
  theme(axis.ticks.x = element_line())

# Test for significant correlation b/w awareness test for omission contingency with low-val colour and capture by low-val colour

low_omission_awareness.cor <- awareness_scores %>%
  filter(question_type == "to_distractor", dType == "Low", colour == "low") %>%
  cor.test(~ Capture + belief_score, data = .)

low_omission_contingency_plot <- awareness_scores %>%
  filter(dType == "Low", colour == "low") %>%
  ggplot(aes(x = belief_score, y = Capture)) +
         geom_point(aes(shape = condition), alpha = .5, size = 3) +
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", colour = "black", size = .5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
  scale_shape_manual(values = c(20,4))+
  labs(x = "Omission contingency belief score", subtitle = "Low reward") +
  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_omission_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
  # facet_grid(~dType) +
  my_theme +
  theme(axis.ticks.x = element_line())

omission_contingency_plots <- plot_grid(high_omission_contingency_plot, low_omission_contingency_plot)

omission_contingency_plots_legend <- plot_grid(omission_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)

# save_plot(here::here("analysis", "figures", "omission_contingency_plot.png"), omission_contingency_plots_legend, ncol = 1.4, nrow = 1.1, type = "cairo")

omission_awareness <- awareness_scores %>%
    group_by(dType,colour) %>%
    count(accuracy) %>%
  mutate(accuracy = case_when(accuracy == 0 ~ "correct",
                              TRUE ~ "incorrect")) %>% 
    pivot_wider(names_from = accuracy, values_from = n) %>% 
  mutate(total = correct + incorrect) %>% 
  filter(dType == "High") %>% 
  ungroup() %>% 
  select(-dType)
